S-Aligner: Ultrascalable read mapping on Sunway Taihu Light

### 2017-04-08 s-aligner.tex
Added Argonne government license.

\author{\IEEEauthorblockN{Xiaohui Duan, Kai Xu, Yuandong Chan}
\IEEEauthorblockA{%College of Computer Science and Technology \\
Shandong University\\
Jinan, China\\
Email: \{sunrise.duan, xu\_kai, yuandong.c\}@mail.sdu.edu.cn}
\and
\IEEEauthorblockN{Christian Hundt, Bertil Schmidt}
\IEEEauthorblockA{Johannes Gutenberg University\\
Mainz, Germany\\
Email: \{hundt, bertil.schmidt\}@uni-mainz.de}
\and
\IEEEauthorblockN{Pavan Balaji}
\IEEEauthorblockA{Argonne National Laboratory\\
Lemont, Illinois, USA\\
Email: balaji@anl.gov}
\and
\IEEEauthorblockN{Weiguo Liu}
\IEEEauthorblockA{Shandong University\\
Jinan, China\\
Email: weiguo.liu@sdu.edu.cn\\
}
}

@@

>>>>

\author{\IEEEauthorblockN{Xiaohui Duan, Kai Xu, Yuandong Chan}
\IEEEauthorblockA{
Shandong University\\
Jinan, China\\
Email: \{sunrise.duan, xu\_kai, yuandong.c\}@mail.sdu.edu.cn}
\and
\IEEEauthorblockN{Christian Hundt, Bertil Schmidt}
\IEEEauthorblockA{Johannes Gutenberg University\\
Mainz, Germany\\
Email: \{hundt, bertil.schmidt\}@uni-mainz.de}
\and
\IEEEauthorblockN{Pavan Balaji}
\IEEEauthorblockA{Argonne National Laboratory\\
Lemont, Illinois, USA\\
Email: balaji@anl.gov}
\and
\IEEEauthorblockN{Weiguo Liu}
\IEEEauthorblockA{Shandong University\\
Jinan, China\\
Email: weiguo.liu@sdu.edu.cn\\
}
}

@@

\vspace{20pt} \footnotesize{The submitted manuscript has been created
  by UChicago Argonne, LLC, Operator of Argonne National Laboratory
  (``Argonne'').  Argonne, a U.S. Department of Energy Office of
  Science laboratory, is operated under Contract
  No. DE-AC02-06CH11357. The U.S. Government retains for itself, and
  others acting on its behalf, a paid-up nonexclusive, irrevocable
  worldwide license in said article to reproduce, prepare derivative
  works, distribute copies to the public, and perform publicly and
  display publicly, by or on behalf of the Government.  The Department
  of Energy will provide public access to these results of federally
  sponsored research in accordance with the DOE Public Access
  Plan. http://energy.gov/downloads/doe-public-access-plan.}
